---
title: "Your 2017-18 NBA Candidates"
author: "Eric Zirzow"
date: "December 13, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(cache=TRUE)

library(tidyverse)
library(bbr)
year<-get_season(2018)
playerRankings <- transmute(year, player, tm, pos, PointsRank=(((pts/g)/20)*.325), ReboundsRank=(((trb/g)/10)*.2), AssistsRank=(((ast/g)/5)*.2), StealsRank=(((stl/g)/1.5)*.1), BlocksRank=(((blk/g)/1)*.1), TurnoversRank=(((tov/g)/3)*.1), PctRank=(((fg_pct)/.5)*.075), OverallRank=PointsRank+ReboundsRank+AssistsRank+StealsRank+BlocksRank-TurnoversRank+PctRank)%>%top_n(15)%>%arrange(desc(OverallRank))
rankingsForTable<-transmute(playerRankings, player, tm, pos, OverallRank)
```
##Introduction
-Analyzed the current NBA season to try to predict the 2017-18 MVP

-Formula includes: Points, Rebounds, Assists, Steals, Blocks, Turnovers, and Shooting Percentage

##Points
-Based off 20

-Weighted at 32.5%
```{r}
points<-filter(year,pts/g>20)
ggplot(data=points)+geom_col(mapping=aes(x=player,y=pts/g, fill=pts))+coord_flip()
```

##Rebounds
-Based off 10

-Weighted at 20%
```{r}
rebounds<-filter(year,trb/g>10)
ggplot(data=rebounds)+geom_col(mapping=aes(x=player,y=trb/g, fill=trb))+coord_flip()
```

##Assists
-Based off 10

-Weighted at 20%
```{r}
assists<-filter(year,ast/g>5)
ggplot(data=assists)+geom_col(mapping=aes(x=player,y=ast/g, fill=ast))+coord_flip()
```

##Steals
-Based off 1.5

-Weighted at 10%
```{r}
steals<-filter(year,stl/g>1.5)
ggplot(data=steals)+geom_col(mapping=aes(x=player,y=stl/g, fill=stl))+coord_flip()
```

##Blocks
-Based off 1.5

-Weighted at 10%
```{r}
blocks<-filter(year,blk/g>1.5)
ggplot(data=blocks)+geom_col(mapping=aes(x=player,y=blk/g, fill=blk))+coord_flip()
```

##Additional Stats
-Turnovers based off 3, weighted at -10%

-FG shooting % based off 50%, weighted at 7.5%

##Top 5 Table
```{r, warning=FALSE, message=FALSE}
knitr::kable(rankingsForTable%>%top_n(5), caption = "Overall Rankings")
```

##Graph of Top 5
```{r}
playerRankings %>% top_n(5) %>% select(-OverallRank) %>% gather(skill, rating, -player, -tm, -pos) %>%
  ggplot(aes(x=skill, y=rating, group=player,color=player))+geom_point()+geom_line()
```

##Verification for last 5 years
-2013: Actual Winner: Lebron James, My winner: LeBron James

-2014: Actual Winner: Kevin Durant, My winner: Kevin Durant

-2015: Actual Winner: Stephen Curry(7), My winner: Anthony Davis(5)

-2016: Actual Winner: Stephen Curry(2), My winner: Russell Westbrook(4)

-2017: Actual Winner: Russell Westbrook, My winner: Russell Westbrook

##Things not factored
-Team Results

-+/-

-Games Played

-Team Changes compounding stats in database